
\subsection*{Liquid Labs (Hyperwave) \hfill Full-Time}
\subtext{Data Lead \hfill June 2025 --- Jan 2026} 
    \begin{zitemize}
        \item Architected and built the Clickhouse MVs and Python data pipeline ingesting data from 75+ DeFi integrations, powering the Portfolio Page showcasing users' DeFi positions and point rewards. 
        \item Modelled the TGE and S2 Airdrop distributions based on point rewards, and bonuses based on community participations
        \item Applied k-means Clustering and DBSCAN to detect sybils, and penalized gains modelled and attributed to sybil activity.
        \item Worked with Community Mods to resolve user data and airdrop queries, with concise technical documentation and visualizations.
        \item Partnered with Operations and Marketing in resolving data requirements for marketing the yield of in-house vaults and tracking operational expenses and revenue via Dune.
    \end{zitemize}

\subsection*{Liquid Labs (Swell Network)  \hfill Full-Time}
\subtext{Data Analyst \hfill Oct 2024 --- Jan 2026} 
    \begin{zitemize}
        \item Rebuilt and scaled the existing points-tracking to track 150+ integrations, rebuilding 2 years of integrations in 2 months, and taking over from Engineering. 
        \item Detected that 80\% of rswETH PT market supply was deposited in Pre-Deposits, directly informing a strategy shift that drove \$500M inflows pushing PreDeposit TVL to \$1.5B.
        \item Partnered with the Strategy Lead in building and testing datasets for EigenLayer, TGE Airdrop. 
        \item Built dashboards tracking liquidity dynamics, operational revenue and expenses, and withdrawals of various Swell products such as Liquid Staking, Liquid Restaking, and Yield-curation Vaults.
        \item Analyzed week-on-week retention of users across all Swell products and proposed incentive framework to reward long-term holders.
        \item Acted as Technical Liaison on all things Swellchain Data. This includes Data integrations on Dune, Flipside, RPC integrations with Goldsky, Nirvana, Ankr, and incentive distribution via Merkl. 
        \item Built a series of dashboards on Flipside tracking revenue and activity of Swellchain and its ecosystem of Dapps
        \item Revamped the existing Python backend powering the Swell Portfolio page, to include Swellchain Integration and Merkl Incentives
    \end{zitemize}